Pilot study Aperol: questionnaire data

### 2021-01-18 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
update questionnaire

```{r overview demographics data table, echo=FALSE}
raw.data %>% # select data
  group_by(session, target, perspective) %>%
  summarise(N = n_distinct(personID),
            male = sum(sex),
            "mean age" = round(mean(age), 2),
            "min age" = min(age),
            "max age" = max(age),
            "sd age" = round(sd(age), 2),
            ) %>% 
  knitr::kable(digits = 2)

@@

```{r plot classroom management boxplot by groups, echo = FALSE}

### classroom management

# filter by parameter variable, i.e. create a subset for each group (expert/novice/experimenter)
km.data <- raw.data %>% filter(scale == "Klassenmanagement")

view (km.data)

# value sometimes contained text before filtering, we have to convert the numbers to numeric
km.data <- km.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# create  mean, min, max, sd of classroom management
meankm <- mean(km.data$value)
minkm <- min(km.data$value)
maxkm <- max(km.data$value)
sdkm <- sd(km.data$value)
Nkm<-length(unique(km.data$ID))
```

>>>>

```{r overview demographics data table, echo=FALSE}
raw.data %>% # select data
  group_by(session, perspective) %>%
  summarise(N = n_distinct(personID),
            "mean age" = round(mean(age), 2),
            "min age" = min(age),
            "max age" = max(age)
            ) %>% 
  knitr::kable(digits = 2)

@@

```{r mean classroom management by session, echo = FALSE}

### classroom management session 1

# filter by parameter variable, i.e. create a subset for each session
km1.data <- raw.data %>% filter(scale == "Klassenmanagement",
                               session == "1")

view (km1.data)

# value sometimes contained text before filtering, we have to convert the numbers to numeric
km1.data <- km1.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# create  mean, min, max, sd of classroom management
meankm1 <- mean(km1.data$value)
minkm1 <- min(km1.data$value)
maxkm1 <- max(km1.data$value)
sdkm1 <- sd(km1.data$value)
Nkm1 <- length(unique(km1.data$personID))
mdkm1 <- median(km1.data$value)

km1.data <- raw.data %>% filter(scale == "Klassenmanagement",
                               session == "1") %>% 
  group_by(perspective, target) %>%
  summarise(N = n_distinct(personID),
            "mean age" = round(mean(age), 2),
            "min age" = min(age),
            "max age" = max(age),
            "sd age" = round(sd(age), 2),
            ) %>% 
  knitr::kable(digits = 2)

### classroom management session 2

# filter by parameter variable, i.e. create a subset for each session
km2.data <- raw.data %>% filter(scale == "Klassenmanagement",
                               session == "2")

view (km2.data)

# value sometimes contained text before filtering, we have to convert the numbers to numeric
km2.data <- km2.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# create  mean, min, max, sd of classroom management
meankm2 <- mean(km2.data$value)
minkm2 <- min(km2.data$value)
maxkm2 <- max(km2.data$value)
sdkm2 <- sd(km2.data$value)
Nkm2<-length(unique(km2.data$personID))

The item "classroom management"  was rated by the observer, the teacher and students on average in session 1 with `r round(meankm1, 2)` (min = `r minkm1`; max = `r maxkm1`; SD = `r round(sdkm1,2)`; N = `r Nkm1`; lickert-scale 1-4; 4 = best evaluation) and in session 2 with `r round(meankm2, 2)` (min = `r minkm2`; max = `r maxkm2`; SD = `r round(sdkm2,2)`; N = `r Nkm2`; lickert-scale 1-4; 4 = best evaluation).

```{r Modul horicontal Plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}

# to create error bars, we need to summarise the data in a seperate dataframe
modul.plot.sd <-modul.plot.data %>%
  group_by(itemfulltext, Teilnehmende, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# and here comes the long plot
modul.plot<-ggplot(data = modul.plot.sd,
                           aes(x = itemfulltext, y = mean,
                               group=Teilnehmende, colour = Teilnehmende)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,5)+
  labs(data = modul.plot.data, y = "Ausprägung", x = NULL,
       title="Modulbewertung" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
modul.plot
